\section{Vectors and Vector Spaces}
\newthought{Vectors are }the most basic and important element in linear algebra. There are several different approaches to defining a vector: physicists like to talk about vectors as objects with magnitude and direction. Computer scientists and programmers tend to view vectors as lists of numbers (and sometimes other types of objects as well). To the mathematician, vectors are elements of \textit{vector sets}, which are defined rigorously and precisely.

The existence of different definitions leads to much confusion\sidenote{I admit that this is a classic case of \enquote{citation needed}, but it is something I come across often.}: for example, we usually think of matrices as \textit{acting} on vectors, so how can matrices be vectors themselves? Also - are vectors just list of numbers, or are there some such lists that aren't vectors? Can we always reduce any vector to a list of numbers? And what about the case of functions as vectors? Etc., etc.

Therefore, for now I choose to limit the definition of vectors to the so-called \enquote{physicist's definition}: a vector is an object which has both a magnitude (also \textit{length} and \textit{norm}), and a direction. These can be easily visualized in 2- and 3-dimensional real spaces as arrows. We will later see how this translates into lists of numbers (and later still how we can define more abstract and inclusive vectors). Since vectors don't have positions, we can freely move them around in space, and normally present them as originating from the same point in space (\cref{fig:vectors}).

\begin{marginfigure}
    \begin{tikzpicture}
    \begin{axis}[
        xyempty,
        width=7cm, height=7cm,
        ]
        \draw[vector={xred}] (0,0) -- (5,2);
        \draw[vector={xblue}] (0,0) -- (-3,5);
        \draw[vector={xgreen}] (0,0) -- (-1,-3);
        \draw[vector={xpurple}] (0,0) -- (1,-4);
        \draw[vector={xorange}] (0,0) -- (4,3);
    \end{axis}
    \end{tikzpicture}
    \caption{Some vectors placed in 2-dimensional space such that they all originate from the same point.}
    \label{fig:vectors}
\end{marginfigure}

Let's now overview the basic operations that can be done with vectors. One operation is \textit{scaling} by a real number: scaling a vector means that we're changing the norm of the vector without changing its direction (\cref{fig:scaling_vectors}). Note that by direction we mean the line going through the vector's origin and its head: when we scale a vector by a negative number $\alpha\in\Rs$ we flip the vector's orientation and scale its norm by the absolute value of $\alpha$ - the vector is then considered to stay in the same direction in space (\cref{fig:scaling_vectors}, again). Generally, the norm of a vector $\vec{u}$ is denoted using double vertical lines: $\vnorm{u}$.

\begin{marginfigure}
    \resizebox{4cm}{!}{
        \begin{tikzpicture}
            \draw[vector={xred}] (0,0) -- ++(1.5,1.5) node[midway, above left] {$\vec{a}$};
            \draw[vector={xblue}] (0,-1) -- ++(3,3) node[midway, above left] {$2\vec{a}$};
            \draw[vector={xgreen}] (0,-2) -- ++(1,1) node[midway, above left, yshift=-7pt] {$\frac{1}{3}\vec{a}$};
            \draw[vector={xpurple}] (1,-2) -- ++(-1.5,-1.5) node[midway, above left] {$-\vec{a}$};
            \draw[vector={xorange}] (1,-3) -- ++(-3,-3) node[midway, above left] {$-2\vec{a}$};
        \end{tikzpicture}
    }
    \caption{Some vectors placed in the origin of a 2-dimensional Cartesian coordinate system.}
    \label{fig:scaling_vectors}
\end{marginfigure}

A vector which has norm of $1$ is called a \textit{unit vector}. We will denote unit vectors in the book using the regular bold notation with a \enquote{hat} on top of it: $\uvec{a}$. Any vector can be made into a unit vector (be \textit{normalized}) by scaling the vector by the reciprocal of its norm (if it isn't zero): given a vector $\vec{u}$, we can scale it by $\vnorm{u}^{-1}$ and get the unit vector $\uvec{u}$, i.e.
\begin{equation}
    \uvec{u} = \frac{1}{\vnorm{u}}\vec{u}.
    \label{eq:label}
\end{equation}

Vectors can also be added together using the \textit{parallelogram rule}: given two vectors $\vec{a}$ and $\vec{b}$ we first place $\vec{b}$ such that its origin lies on the head of $\vec{a}$. The vector $\vec{c}$ from the origin of $\vec{a}$ to the head of $\vec{b}$ is the result of the addition.
